%-------------------------
% Cover Letter in LaTeX
% Author: Bibhab Pattnayak
%------------------------

\documentclass[11pt]{letter}

\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage[pdftex, hidelinks]{hyperref}
\usepackage[charter]{mathdesign}
\usepackage{geometry}

\geometry{
    left=1in,
    right=1in,
    top=0.75in,
    bottom=0.75in
}

\pdfgentounicode=1

\begin{document}

\begin{center}
    \textbf{\Large Bibhab Pattnayak} \\
    \vspace{4pt}
    Redmond, WA \hspace{4pt}$\vert$\hspace{4pt}
    \href{mailto:bibhabpattnayak@gmail.com}{bibhabpattnayak@gmail.com} \hspace{4pt}$\vert$\hspace{4pt}
    480-955-9942
\end{center}

\vspace{12pt}

\noindent
\today

\vspace{12pt}

\noindent
Apple Inc. \\
Information Systems \& Technology \\
Role Number: 200620195-0836

\vspace{12pt}

\noindent
Dear Hiring Team,

\vspace{8pt}

\noindent
I am writing to express my interest in the Senior Software Engineer position within Apple's Information Systems \& Technology group. With 7+ years of experience designing and shipping high-scale distributed systems in Java, and a track record of building fault-tolerant services that process millions of daily requests, I am excited about the opportunity to contribute to the systems that power Apple's operations and customer experiences.

\vspace{8pt}

\noindent
In my current role at AWS, I develop features for AWS Glue Data Catalog—a multi-tenant system handling 10M+ daily API requests across 35 global regions. I designed a resource-based throttling system that reduced critical availability incidents by 80\%, and I build RESTful APIs while contributing to schema design and query optimization. This work directly maps to what IS\&T needs: engineers who can build reliable, secure, cloud-based distributed systems at scale.

\vspace{8pt}

\noindent
Beyond technical execution, I bring the collaboration and leadership qualities the role requires. I championed a shift-left testing strategy that cut deployment cycles by 40\% and accelerated delivery across three dependent teams. I mentor engineers on distributed systems design patterns and lead design reviews focused on testable, maintainable code. At VMware, I designed observability platforms serving 2,000+ data centers and delivered \$400K in annual savings through strategic architecture decisions.

\vspace{8pt}

\noindent
What draws me to Apple is the scope and impact of IS\&T's work—from apple.com to Apple Care to enterprise-wide data processing systems. The opportunity to build software that both customers and employees rely on daily, while working alongside world-class engineers, is compelling. I am particularly interested in contributing to Apple's data processing and AI/ML infrastructure, where my experience with high-throughput pipelines and fault-tolerant design would translate directly.

\vspace{8pt}

\noindent
I would welcome the opportunity to discuss how my background in building scalable Java systems, designing APIs, and leading technical initiatives aligns with your team's goals. Thank you for considering my application.

\vspace{16pt}

\noindent
Sincerely,

\vspace{24pt}

\noindent
Bibhab Pattnayak

\end{document}
